---
title: "Task 05: Quiz"
author: "Mark Blackmore"
date: "November 8, 2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("05_Task_Script.R")
```

For each of the sentence fragments below use your natural language processing algorithm to predict the next word in the sentence.

Q1. When you breathe, I want to be the air for you. I'll be there for you, I'd live and I'd  

  * sleep
  * give
  * die
  * eat

```{r}
ngrams("When you breathe, I want to be the air for you. I'll be there for you, I'd live and I'd")
```
  
Q2. Guy at my table's wife got up to go to the bathroom and I asked about dessert and he started telling me about his  

  * horticultural
  * marital
  * spiritual
  * financial

```{r}
ngrams("Guy at my table's wife got up to go to the bathroom and I asked about dessert and he started telling me about his")
```

Q3. I'd give anything to see arctic monkeys this  

  * weekend
  * decade
  * month
  * morning

```{r}
ngrams("I'd give anything to see arctic monkeys this")
```

Q4. Talking to your mom has the same effect as a hug and helps reduce your  

  * sleepiness
  * happiness
  * hunger
  * stress

```{r}
ngrams("Talking to your mom has the same effect as a hug and helps reduce your")
```

Q5. When you were in Holland you were like 1 inch away from me but you hadn't time to take a  

  * walk
  * minute
  * look
  * picture
  
```{r}
ngrams("When you were in Holland you were like 1 inch away from me but you hadn't time to take a")
```
  
Q6. I'd just like all of these questions answered, a presentation of evidence, and a jury to settle the

  * account
  * case
  * matter
  * incident
  
```{r}
ngrams("I'd just like all of these questions answered, a presentation of evidence, and a jury to settle the")
```
  
Q7. I can't deal with unsymetrical things. I can't even hold an uneven number of bags of groceries in each  

  * hand
  * finger
  * toe
  * arm

```{r}
ngrams("I can't deal with unsymetrical things. I can't even hold an uneven number of bags of groceries in each")
```

Q8. Every inch of you is perfect from the bottom to the  

  * top
  * middle
  * center
  * side

```{r}
ngrams("Every inch of you is perfect from the bottom to the")
```

Q9. I'm thankful my childhood was filled with imagination and bruises from playing  

  * weekly
  * inside
  * outside
  * daily

```{r}
ngrams("I'm thankful my childhood was filled with imagination and bruises from playing ")
```

Q10. I like how the same people are in almost all of Adam Sandler's  

  * movies
  * stories
  * pictures
  * novels
  
```{r}
ngrams("I like how the same people are in almost all of Adam Sandler's")
```
  
  